Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-06-23 Setup/report.tex
Rename program from PSI to BONSAY

\section{Codes}
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(g_W^6)$ $s/t/u$  &  $\mathcal O(g_W^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(g_W^4g_s^2)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc PSI}     &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
    \end{tabularx}
    \caption{\label{tab:codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}

@@

\begin{table}[h!]
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
        {\sc PSI}     &  $1.5524 \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
    \end{tabular}
    \caption{\label{tab:LOrates} LO rates within VBS cuts from the different codes.}
\end{table}

@@

\begin{table}[h!]
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  &  $\sigma(n_j=2)[\rm{fb}]$  &  $\sigma(n_j=3)[\rm{fb}]$\\
        \hline
        \hline
        {\sc POWHEG}  &  \\
        {\sc Recola}  &  \\
        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
        {\sc PSI}     &  \\
        {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\
    \end{tabular}
    \caption{\label{tab:NLOrates} NLO rates within VBS cuts from the different codes.}
\end{table}

>>>>

\section{Codes}
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(g_W^6)$ $s/t/u$  &  $\mathcal O(g_W^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(g_W^4g_s^2)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
    \end{tabularx}
    \caption{\label{tab:codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}

@@

\begin{table}[h!]
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
        {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
    \end{tabular}
    \caption{\label{tab:LOrates} LO rates within VBS cuts from the different codes.}
\end{table}

@@

\begin{table}[h!]
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  &  $\sigma(n_j=2)[\rm{fb}]$  &  $\sigma(n_j=3)[\rm{fb}]$\\
        \hline
        \hline
        {\sc POWHEG}  &  \\
        {\sc Recola}  &  \\
        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
        {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\
    \end{tabular}
    \caption{\label{tab:NLOrates} NLO rates within VBS cuts from the different codes.}
\end{table}
